This is an example of article title

### 2025-10-28 paper/paper.tex
Fix one small error on manifolds for circle.

For the \verb|CircleGroup()|, three different representations of points are available: as angles in \([0, 2\pi)\), as complex numbers with unit norm, and as points on the unit circle in \(\mathbb{R}^2\).
These are constructed by specifying the representation of points, i.e. \verb|CircleGroup(|$\mathbb R$\verb|)|, \verb|CircleGroup(|$\mathbb C$\verb|)|, and \verb|CircleGroup(|$\mathbb R^2$\verb|)|, respectively. Note that each of these representations uses a different underlying manifold, namely \verb|Circle(|$\mathbb R$\verb|)|, \verb|Circle(|$\mathbb C$\verb|)|, and \verb|Circle(|$\mathbb R^2$\verb|)|, respectively.
This is a case, where it is not only the representation of points and tangent vectors that differ, but indeed even the underlying manifold.

@@

{\color{red}TODO: Brainstorm over one or two examples with code.}

\input{bib.tex}
\end{document}
%
% ------------------------------------------------------------------------------------------
%

\subsection{Writing Julia code}

A special environment is already defined for Julia code,
built on top of \textit{listings} and \textit{jlcode}.

\begin{verbatim}
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:exmplg},
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}
\end{verbatim}
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:exmplg},
    caption={Example Code Block.}
]
using Plots

x = -3.0:0.01:3.0
y = rand(length(x))
plot(x, y)
\end{lstlisting}

\subsection{Balancing column at last page}
\label{subsub:Balance}
For balancing the both column length at last page use :
\begin{verbatim}
\vadjust{\vfill\pagebreak}
\end{verbatim}

%\vadjust{\vfill\pagebreak}

at appropriate place in your \TeX{} file or in bibliography file.

>>>>

For the \verb|CircleGroup()|, three different representations of points are available: as angles in \([0, 2\pi)\), as complex numbers with unit norm, and as points on the unit circle in \(\mathbb{R}^2\).
These are constructed by specifying the representation of points, i.e. \verb|CircleGroup(|$\mathbb R$\verb|)|, \verb|CircleGroup(|$\mathbb C$\verb|)|, and \verb|CircleGroup(|$\mathbb R^2$\verb|)|, respectively. Note that each of these representations uses a different underlying manifold, namely \verb|Circle(|$\mathbb R$\verb|)|, \verb|Circle(|$\mathbb C$\verb|)|, and \verb|Sphere(1)|, respectively.
This is a case, where it is not only the representation of points and tangent vectors that differ, but indeed even the underlying manifold.

@@

{\color{red}TODO: Do a Forward Euler simulation on a nice physics problem}

\input{bib.tex}
\end{document}
